### 2023-06-29 paper/main.tex
matlab_added

\section{Comparison with direct modal bandlimitation}
Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation.

@@

\begin{figure*}[h!]
    \begin{center}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center.png}
            \footnotesize \put(0,2){(a)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_right.png}
            \footnotesize \put(0,2){(b)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_front.png}
            \footnotesize \put(0,2){(c)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
            \footnotesize \put(0,2){(d)}
        \end{overpic}\\  \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_center.png}
            \footnotesize \put(0,2){(e)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_left.png}
            \footnotesize \put(0,2){(f)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
            \footnotesize \put(0,2){(g)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_back.png}
            \footnotesize \put(0,2){(h)}
        \end{overpic}\\ \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_center.png}
            \footnotesize \put(0,2){(i)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_left.png}
            \footnotesize \put(0,2){(j)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
            \footnotesize \put(0,2){(k)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_back.png}
            \footnotesize \put(0,2){(l)}
        \end{overpic}\\
    \end{center}
    \caption{fg}
    \label{Fig:aliasing}
\end{figure*}

>>>>

\section{Comparison with direct modal bandlimitation}
\begin{figure*}[h!]
    \begin{center}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center2.png}
            \footnotesize \put(0,2){(a)}
            \footnotesize \put(45,102){Center}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_left2.png}
            \footnotesize \put(0,2){(b)}
            \footnotesize \put(45,102){Left}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_front.png}
            \footnotesize \put(0,2){(c)}
            \footnotesize \put(45,102){Front}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
            \footnotesize \put(0,2){(d)}
            \footnotesize \put(45,102){Back}
        \end{overpic}\\  \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_center.png}
            \footnotesize \put(0,2){(e)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_left.png}
            \footnotesize \put(0,2){(f)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
            \footnotesize \put(0,2){(g)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_back.png}
            \footnotesize \put(0,2){(h)}
        \end{overpic}\\ \vspace{5mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_center.png}
            \footnotesize \put(0,2){(i)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_left.png}
            \footnotesize \put(0,2){(j)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
            \footnotesize \put(0,2){(k)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_back.png}
            \footnotesize \put(0,2){(l)}
        \end{overpic}\\
    \end{center}
    \caption{Comparison of the proposed, temporal filtering/based LWFS approach with direct modal bandlimitation.
    }
    \label{Fig:aliasing}
\end{figure*}

Finally, the performance of the proposed Local Wave Field Synthesis approach is compared with conventional a LWFS implementation, based on direct modal bandlimitation.

@@
